---
title: "R Assignment Report"
author: "Zhuo Zhao 100636803 Undergraduate Student"
date: "April 19, 2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
rm(list = ls())
gc()
library(dplyr)
library(ggplot2)
library(reshape2)

fed <- read.csv("fed_r_d_spending.csv")
climate <- read.csv("climate_spending.csv")
energy <- read.csv("energy_spending.csv")
``` 
### Fed R&D Data

#### Total R&D Budget and GDP

```{r echo= FALSE}
# Create a new column summarizing the total R&D budget
fed_summarized <- group_by(fed, year) %>%
  summarise(total_rd = sum(rd_budget))

fed_new <- left_join(fed, fed_summarized, by = 'year')

# Plot the relationship between Total RD and GDP
p <- ggplot(fed_new, aes(x = total_rd, y = gdp, color = year))

p + geom_point(size = 3) + labs(x = "Total R&D Budget", color = "Year", y = "GDP") +
  ggtitle("Total R&D Budget and GDP") + geom_smooth(method = "lm")

```
<p>The graph shows that the relationship between R&D Budget and GDP is positive, which indicates the investment in R&D may promote the growth of GDP.</p>
<p>Also, we can see the GDP and Total R&D Budget are increasing over time.</p> 

#### R&D Budgets in Different Departments
<p> How much are the R&D budgets in different department? Are R&D budgets increasing as time goes by?

```{r echo = FALSE, warning = FALSE}
p <- ggplot(fed_new, aes(x=year, y = rd_budget, color = department))
sequence <- filter(fed_new, year == max(year)) %>% arrange(desc(rd_budget)) %>%
  select(department)

p + geom_point() + geom_smooth(method = 'lm') + 
  labs(x = 'Year', y = 'R&D Budget', title = 'R&D in Different Departments',
       color = "Departments") + 
  scale_color_discrete(breaks = sequence[[1]]) + scale_y_log10() + xlim(1976,2018)

  
```
As we can see, not all departments have increasing R&D budgets over time. And the Department of Defense has the highest the R&D budgets all the time. 

#### Discretionary Outlays and Total Outlays
```{r echo = FALSE}
fed_new_sub = fed_new[,c("year", "total_outlays",
                         "discretionary_outlays")]

mask <- !duplicated(fed_new_sub)

fed_new_sub <- fed_new_sub[mask,]

fed_new_sub <- melt(fed_new_sub,id = c("year"))

p <- ggplot(fed_new_sub, aes(x = year, y = value, 
                             color = variable))
p + geom_point() + geom_smooth(method = 'lm') + 
  labs(x = "Year", y = "Value", color = "", 
       title = "Total Outlays vs Discretionary Outlays") +
  scale_color_discrete(labels = c("Total Outlays", "Discretionary Outlays"))

```
<p>Generally, both total outlays and discretionary outlays are increasing over time. And the growth rate of total outlays is larger than the discretionary outlays.<p>

### Climate and Energy Spendings Data
#### GCC and Energy Spendings Summary 
```{r, echo = FALSE}
p <- ggplot(climate, aes(x = year, y = gcc_spending, 
                         color = department))

sequence <- filter(climate, year == max(year)) %>%
  arrange(desc(gcc_spending)) %>% select(department)

p + geom_point() + geom_smooth(method = "lm") + 
  scale_y_log10() + 
  labs(x = "Year",y = "GCC Spending",
       title = "GCC Spendings Over Time", 
       color = "Department") +
  scale_color_discrete(breaks = sequence[[1]])
  
            
```
```{r echo= FALSE}
p <- ggplot(energy, aes(x = year, y = energy_spending, 
                         color = department))

sequence <- filter(energy, year == max(year)) %>%
  arrange(desc(energy_spending)) %>% select(department)

p + geom_point() + geom_smooth(method = "lm") + 
  labs(x = "Year",y = "Energy Spending",
       title = "Energy Spendings Over Time", 
       color = "Department") +
  scale_color_discrete(breaks = sequence[[1]])
```


#### What is the relationship between climate spendings and energy Spendings?

```{r echo = FALSE}
climate_group <- group_by(climate, year) %>%
  summarise(gcc_total = sum(gcc_spending))

energy_group <- group_by(energy, year) %>% 
  summarise(energy_total = sum(energy_spending))

climate_energy <- inner_join(climate_group, energy_group, by = "year")

climate_energy <- melt(climate_energy, id = 'year')

p <- ggplot(climate_energy, aes(x = year, y = value, color = variable))

p + geom_line() + 
  labs(x = "Year", y = "Value", color = "", 
       title = "Total GCC and Energy Spendings Over Time") + 
  scale_color_discrete(labels= c("Total GCC Spendings", 
                                 "Total Engery Spendings"))

climate_energy <- dcast(climate_energy, year ~ variable)
p <- ggplot(climate_energy, aes(x = gcc_total, y = energy_total,
                                color = year))
p + geom_point(size = 2) + geom_smooth(method = 'lm') + 
  labs(x = "Total GCC Spendings", y = "Total Energy Spendings",
       color= "Year", 
       title = "Energy Spendings Vs GCC Spendings")



```

The GCC spending may have positive relationship with energy spending. But it needs hypothesis test to prove it. 
