---
title: "Fed R&D Research Report"
author: "Zhuo Zhao"
date: "April 12, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
rm(list = ls())
gc()
library(dplyr)
library(ggplot2)

fed <- read.csv("fed_r_d_spending.csv")
``` 
### Brief Introduction
This report mainly focuses on the R&D data set. 

### Total R&D Budget and GDP

```{r echo= FALSE}
# Create a new column summarizing the total R&D budget
fed_summarized <- group_by(fed, year) %>%
  summarise(total_rd = sum(rd_budget))

fed_new <- left_join(fed, fed_summarized, by = 'year')

# Plot the relationship between Total RD and GDP
p <- ggplot(fed_new, aes(x = total_rd, y = gdp, color = year))

p + geom_point(size = 3) + labs(x = "Total R&D Budget", color = "Year", y = "GDP") +
  ggtitle("Total R&D Budget and GDP") + geom_smooth(method = "lm")

```
<p>The graph shows that the relationship between R&D Budget and GDP is positive, which indicates the investment in R&D may promote the growth of GDP.</p>
<p>Also, we can see the GDP and Total R&D Budget are increasing.</p> 

### R&D Budget三 in Different Departments
<p> What are the R&D budgets in different department? Are R&D budgets increasing as time goes by?

```{r echo = FALSE, warning = FALSE}
p <- ggplot(fed_new, aes(x=year, y = rd_budget, color = department))
sequence <- filter(fed_new, year == max(year)) %>% arrange(desc(rd_budget)) %>%
  select(department)

p + geom_point() + geom_smooth(method = 'lm') + 
  labs(x = 'Year', y = 'R&D Budget', title = 'R&D in Different Departments',
       color = "Departments") + 
  scale_color_discrete(breaks = sequence[[1]]) + scale_y_log10() + xlim(1976,2018)

  
```
As we can see, not all departments have increasing R&D budgets over time. And the Department of Defense has the highest the R&D budgets all the time. 

### Discretionary Outlays and Total Outlays
```{r echo = FALSE}
```